---
title: "R Notebook"
output: html_notebook
---

```{r}
library(jsonlite)
library(dplyr)
library(utils)
library(stringi)
```

```{r}
# This merges the cfimdb and base files so that they exist in one csv file

csfimdb <- read.delim("ids-cfimdb-train.csv")
base <- read.delim("ids-sst-train.csv")

# Transform labels of cfimdb
csfimdb$sentiment = ifelse(csfimdb$sentiment == 1, 4, 0)

df_merged <- rbind(base, csfimdb)
df_merged <- df_merged %>%
  select(id, sentence, sentiment)

# Make sure that csv is tab delimited
write.table(df_merged, "ids-sst-train-merged.csv", row.names = FALSE, sep="\t")
```

```{r}
# Adds duplicate question dataset 


duplicate_questions_raw <- fromJSON("stackexchange_duplicatequestions.json")
colnames(duplicate_questions_raw) <- c("sentence1", "sentence2")

set.seed(123)

duplicate_questions <- as.data.frame(duplicate_questions_raw,
                                     row.names = c("sentence1", "sentence2"))

# Generate random ids
duplicate_questions$id <- stri_rand_strings(nrow(duplicate_questions), 
                                            25,
                                            pattern="[0-9a-f]")
duplicate_questions <- duplicate_questions %>%
  mutate(similarity = 4.0) %>%
  select(id, sentence1, sentence2, similarity)

# Just get the first 1000 observations
duplicate_questions <- duplicate_questions[0:1000,]

# Make sure that csv is tab delimited
write.table(df_merged, "ids-sts-train-duplicate-questions.csv", 
            row.names = FALSE, sep="\t")


```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

